---
title: "Effect of Maternal Gender-Biased Speech on Children’s Gender Socialization"
author:
  - name: Kaiwen Yang
    email: kaiweny@uchicago.edu
shorttitle: from D2M course
bibliography: "r-references.bib"
output: papaja::apa6_pdf


header-includes:
  - \usepackage{colortbl}
---

```{r setup, include = FALSE, echo=FALSE}
# r package library
library(papaja)
r_refs("r-references.bib")
library(tidyverse)
library(knitr)
library(tinytex)
library(kableExtra)
```
# Introductions

Numerous studies in recent decades have demonstrated that gender role socialization starts from birth [e.g., @birnsEmergenceSocializationSex1976; @honigSexRoleSocialization1983]. Parents play a crucial role in influencing their children to engage in gender role stereotyped activities, and that these perceptual biases influence the children’s own self-perceptions and activity choices [@ecclesGenderRoleStereotypes1990].  

In the field of language development, researchers have postulated that Infant-Directed Speech (IDS) is an ideal signal for language learning due to infants’ strong preference for it, providing attentional, emotional, linguistic, and social cues [@ferjanramirezFathersInfantdirectedSpeech2022]. Recent studies examining language input to boys and girls reveal distinct biases in IDS content, with boys exposed more to words associated with outdoor scenes and girls to terms related to clothing and body parts [@kachergisEstimatingDemographicBias2023; @wallentinCrossCulturalSexGender2023]. Parents tend to discuss emotions more with girls than boys [@adamsGenderDifferencesParentchild1995a], explain scientific content more to boys in certain settings [@crowleySharedScientificThinking2001], and engage in cognitive development-promoting discussions more frequently with boys [@weitzmanTraditionalNontraditionalMothers1985]. 

Although parental interactions, name choices, and attire vary based on their children’s sex, they are all crucial in shaping gender identity, and carry profound implications for cognitive processes and linguistic development [@GenderIdentityChildhood]. Infants demonstrate an early awareness of gender differences, showing preferences for gender-associated objects within the first year [@levyDetectionGenderrelatedCategories1994]. By age 3, most children exhibit awareness of gender stereotypes, influencing their preferences and behaviors [@martinRelationGenderUnderstanding1990]. Moreover, children increasingly regulate their behavior based on these gender-based conceptions once they develop a sense of their gender identity [@busseySocialCognitiveTheory1999]. @powlishtaGenderBiasChildren1995 demonstrates that despite own-sex favoritism, children between 8 and 10 years old already have differing views of the masculinity or femininity of personality traits. Both boys and girls ascribe certain personality attributes as masculine or feminine. Traits such as “polite”, “shares”, “soft-hearted”, “gentle”, “affectionate”, “gloomy”, and “cries” are perceived as feminine whereas qualities like “bold”, “strong”, “messy”, “fights”, “cruel”, “loud”, and “crude” are associated with masculinity. This divide aligns with the Stereotype Content Model [@cuddyWarmthCompetenceUniversal2008]. Researchers have also identified distinction between stereotypically feminine communal traits (matching the warmth dimension) and stereotypically masculine agentic traits (matching the competence dimension; @cuddyWarmthCompetenceUniversal2008).  
Despite this rich understanding, little is known about how gender-biased IDS from parents influences children's development of gender concepts.
It is vital for us to ask these questions because biases in parental communication can significantly shape children's attitudes towards relationships, educational equality, career aspirations, and overall well-being [@weiGenderDifferencesPreschool2009].


# Methods
The current study will re-analyze data from the CHILDES (Child Language Data Exchange System) database, the child language component of the TalkBank system. The CHILDES includes transcripts of child language in 26 languages from 230 different corpora which record spontaneous conversational interactions between young monolingual children and their parents, playmates, and teachers. 
Measures
Child sex. This variable will be determined based on the infant information (“Target_Child’s sex”: male; female) provided in the CHILDES database.
Gender-biased nouns. Nouns extracted from the two lists “Top 10 most female/male biased words in English (America) for comprehension data” of the Wordbank data report (2016) will be treated as gender-biased language data. We will calculate the percentage of nouns in each transcript that meets these criteria.
Competence and warmth adjectives. Based on the SCM’s categorization (2008), warmth scales include “good‐natured”, “trustworthy”, “tolerant”, “friendly”, and “sincere”, whereas competence scales include “capable”, “skillful”, “intelligent”, and “confident”. We will calculate the percentage of adjectives within each transcript that comes from these scales.
## Analysis Plan
Using statistical analyses, specifically t-tests, we will compare the occurrence rates of gender-biased nouns and adjectives from mothers’ IDS towards male and female infants. To ascertain the significance of the observed differences while considering the multiplicity of comparisons, corrections for multiple comparisons such as Bonferroni or False Discovery Rate (FDR) adjustments will be applied. This step ensures the maintenance of an appropriate overall alpha level, minimizing the possibility of chance findings due to conducting numerous tests.
Subsequently, a multivariate analysis will be conducted to assess the combined influence of child sex, child age, and maternal language type. 
The ultimate goal is to discern any significant differences in language usage based on child sex, specifically examining the presence and frequency of gender-biased and gender-neutral vocabulary, as well as competence and warmth-related trait descriptors in maternal speech directed towards male and female infants. This approach will offer insights into how gendered language patterns contribute to early gender socialization processes.


# Data analysis

```{r male-nouns, echo=FALSE}

m.data <- read.csv("//Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/Proportion data/noun_proportion_data.csv")

ggplot(m.data, aes(x = target_child_sex, y = mnoun_proportion, fill = target_child_sex)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.5, aes(colour = target_child_sex)) +
  scale_fill_manual(values = c("female" = "lightpink", "male" = "lightblue")) +
  labs(x = "Gender", y = "Proportion", title = "Male-Biased Noun Proportion", fill = "Sex of Child", colour = "Sex of Child") +
   theme(
  strip.background = element_rect(fill = "gray60"),
  panel.grid = element_line(colour = "white", linetype = 3),
  legend.title = element_text(size = 10),
  strip.text = element_text(colour = "white", hjust = 0),
  legend.position = "bottom"
)
  
```

X-axis: The gloss variable, representing different words (like "dress", "doll", "necklace", etc.). Y-axis: The count or frequency of each word, indicating how often each word appears in the dataset. Type of Plot: Bar Chart. Comparison Across Groups?: Yes Anticipated Findings: mothers speak more female-biased nouns to female infants than to male infants

As seen in Figure \@ref(fig:my-figure), There's gender bias in the nouns of mother's infant-directed speech.

# Prettified Plot

```{r my-figure, echo=FALSE, fig.cap="Proportion of Gender-Biased Nouns by Gender"}
combined.data <- read.csv("//Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/Proportion data/noun_proportion_data.csv")

library(tidyr)
long_data <- combined.data %>%
  pivot_longer(cols = c(mnoun_proportion, fnoun_proportion),
               names_to = "type",
               values_to = "proportion")
labels_gender = c('fnoun_proportion' = "Female-Biased", 'mnoun_proportion' = "Male-Biased")

ggplot(long_data, aes(x = target_child_sex, y = proportion, fill = target_child_sex)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.5, aes(colour = target_child_sex)) +
  scale_fill_manual(values = c("female" = "lightpink", "male" = "lightblue")) +
  facet_wrap(~type, scales = "fixed", labeller = as_labeller(labels_gender)) +
  labs(title = "Proportion of Gender-Biased Nouns", x = "Gender", y = "Proportion", fill = "Sex of Child", colour = "Sex of Child")+
  theme(
  strip.background = element_rect(fill = "gray60"),
  panel.grid = element_line(colour = "white", linetype = 3),
  legend.title = element_text(size = 10),
  strip.text = element_text(colour = "white", hjust = 0),
  legend.position = "bottom"
)
```

X-axis: female/male infants\
Y-axis: counts of frequency of female-biased nouns Type of Plot: box plot\
Comparison Across Groups?: Yes\
Anticipated Findings: mothers speak more female-biased nouns in CDS to female infants than to male infants


```{r my-table, echo=FALSE, warning=FALSE, tab.cap="my-table"}
knitr::kable(m.data,
             format = "latex",
             booktabs = TRUE, 
             caption = "Male-Infant Data", 
             label = "my-table") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE, color = "blue") %>%
  row_spec(0, bold = TRUE, background = "#D3D3D3")

```

As shown in Table \@ref(tab:my-table), the gender distribution in the dataset varies, with a higher percentage of Female compared to Male.


## *Descriptive Analysis*: Examining Maternal Gender-Biased Language Imput Patterns

```{r summary-stats, echo=FALSE}
library(psych)
library(lme4)

   ## In this analysis, I aim to describe the patterns of gender-biased language usage by mothers in interactions with their children. The analysis will focus on:
   ### - The frequency of appearance-related adjectives (e.g., "pretty", "beautiful") and competence-related adjectives (e.g., "strong", "smart") used by mothers when speaking to boys vs. girls.
   ### - The frequency of gender-biased nouns (e.g., "truck" for boys, "doll" for girls) used by mothers in their speech to children of different genders.

  ## Independent Variables: Child's gender (binary: male or female)

# Calculate descriptive statistics for male-biased nouns
noun_tidied_count <- read.csv("/Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/Proportion data/noun_proportion_number.csv")

summary_mnoun <- noun_tidied_count %>%
  group_by(target_child_sex) %>%
  summarise(mean_mnoun = mean(mnoun_proportion),
            median_mnoun = median(mnoun_proportion),
            sd_mnoun = sd(mnoun_proportion),
            .groups = 'drop')

# Print the summary statistics
print(summary_mnoun)

library(tidyr)
long_data <- noun_tidied_count %>%
  pivot_longer(cols = c(mnoun_proportion, fnoun_proportion),
               names_to = "type",
               values_to = "proportion")
labels_gender = c('fnoun_proportion' = "Female-Biased", 'mnoun_proportion' = "Male-Biased")
```

```{r gender-nouns, echo=FALSE}
#Visualization of all stats

ggplot(long_data, aes(x = target_child_sex, 
                      y = proportion, 
                      fill = target_child_sex), 
       label = "gender-nouns") +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.5, aes(colour = target_child_sex)) +
  scale_fill_manual(values = c("female" = "lightpink", "male" = "lightblue")) +
  labs(x = "Gender", y = "Proportion", fill = "Sex of Child", colour = "Sex of Child") +
  facet_wrap(~type, scales = "fixed", labeller = as_labeller(labels_gender)) +
  labs(title = "Proportion of Gender-Biased Nouns")+
  theme(
  panel.grid = element_line(colour = "white", linetype = 3),
  legend.title = element_text(size = 10),
  strip.background = element_rect(fill = "gray60"),
  strip.text = element_text(colour = "white", hjust = 0),
  legend.position = "bottom"
)

  ## Dependent Variables:
  ### - Percentage of gender-biased adjectives (appearance-related and competence-related) in maternal language input.
  ### - Percentage of gender-biased nouns in maternal language input.

```

As shown in Figure \@ref(fig:gender-nouns), this descriptive analysis will involve calculating means and standard deviations for the usage of gender-biased language across mothers of boys and girls. We will visualize these patterns through box and jitter plots to identify any apparent differences in language input based on the child's gender.


## *Hypothesis Testing Analysis*: Testing the Influence of Child's Gender on Maternal Language Input

```{r hypothesis-analysis, echo=FALSE}
library(stats)
noun_tidied_count <- read.csv("/Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/Proportion data/noun_proportion_number.csv")
# ANOVA for male-biased nouns
anova_mnoun <- aov(mnoun_proportion ~ target_child_sex, data = noun_tidied_count)
summary(anova_mnoun)

# ANOVA for female-biased nouns
anova_fnoun <- aov(fnoun_proportion ~ target_child_sex, data = noun_tidied_count)
# Get the summary of the ANOVA result
summary(anova_fnoun)
tukey_results <- TukeyHSD(anova_fnoun)

  ## Hypothesized Results: It is hypothesized that there will be a significant difference in the percentage of gender-biased language (both adjectives and nouns) used by mothers, with a higher use of appearance-related words for girls and competence-related words for boys, as well as a higher usage of gender-congruent nouns (male-biased with boys, female-biased with girls).
  
  ## Appropriate Tests: For comparing multiple variables between two groups (boys vs. girls), *ANOVA* could be appropriate for continuous data (e.g., percentage of gender-biased words). 

  ### This analysis will help determine if there is a statistically significant difference in maternal language input that could contribute to the early formation of gender stereotypes and expectations in children.

```


The ANOVA tests conducted on the proportions of female-biased nouns used by mothers reveal the following: 
The Tukey test results are: 
`r knitr::kable(tukey_results$target_child_sex, caption = "Tukey HSD Test Results for Target Child Sex")`

For female-biased nouns used by mothers, the F-statistic is $F$ = `r round(summary(anova_fnoun)[[1]]$F[1],3)`, $p$ = `r round(summary(anova_fnoun)[[1]]$P[1],3)`.


And for male-biased nouns used by mothers, the F-statistic is $F$ = `r round(summary(anova_mnoun)[[1]]$F[1],3)`, $p$ = `r round(summary(anova_mnoun)[[1]]$P[1],3)`.

The results suggest that there is a statistically significant difference in the usage of gender-biased nouns by mothers when speaking to male children compared to female children, at the conventional 0.05 significance level.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
