---
title             : "My Notebook"
shorttitle        : "from D2M course"

author: 
  - name          : "Katia Yang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "kaiweny@uchicago.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : html_document
---

```{r source-script}
source("My_Script.R")
```

<!-- Assignment 5 -->

```{r call-function}
# Call the hello_world function
result1 <- hello_world("Dr.Dowling")
result2 <- hello_world("Voldemort")
result3 <- hello_world("Wubalubadubdub")

# Print the results
print(result1)
print(result2)
print(result3)
```

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```


# Methods

### dataset

```
6 Corpuses from the **CHILDES** 
URL:[<https://childes.talkbank.org/>]

## Material

## Participants

Participants including *6 children*:   
1. Alex  
   a. Alex's mother
2. Violet  
   a. Violet's father
3. Naima  
4. Lily  
5. William  
6. Ethan  

<!-- I don't know what to write --> 
And these characters: 

* Adventure Time
  - Finn
  - Jack
  - BMO
  - Princess Bubblegum
  - Ice King
* Rick and Morty
  - Rick
  - Morty
    + Morty 233
    + Morty 167
  - Summer

## Procedure

## Data analysis
### Assignment (10)
### 10.1
```{r mock up female biased nouns plots}

library(ggplot2)
install.packages("reshape2")
library(reshape2)

data <- read.csv("/Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/tidy data/counts_fnouns.csv")

long_data <- melt(data, id.vars = "gloss")

ggplot(long_data, aes(x = gloss, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_minimal() +
  labs(x = "Word", y = "Count", fill = "Gender",
       title = "Frequency of Female Gender-biased Nouns",
       subtitle = "Comparing the frequency of gender-biased maternal CDS between female and male infants") +
  scale_fill_manual(values = c("female" = "pink", "male" = "lightblue"))

# X-axis: The gloss variable, representing different words (like "dress", "doll", "necklace", etc.).
# Y-axis: The count or frequency of each word, indicating how often each word appears in the dataset.
# Type of Plot: Bar Chart. 
# Comparison Across Groups?: Yes
# Anticipated Findings: mothers speak more female-biased nouns to female infants than to male infants
```
###10.2
```{r mock up Female-biased Nouns Plot}

proportion_fnoun <- read.csv("/Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/Proportion data/fnoun_number_proportions.csv")

ggplot(proportion_fnoun, aes(x = target_child_sex, y = fnoun_proportion, fill = target_child_sex)) +
  geom_boxplot(alpha = 0.5) +
  scale_fill_manual(values = c("female" = "lightpink", "male" = "lightblue")) +
  labs(x = "Gender", y = "Proportion", title = "Female-Biased Noun Proportion") +
  theme_minimal()

# X-axis: female/male infants
# Y-axis: counts of frequency of female-biased nouns
# Type of Plot: box plot
# Comparison Across Groups?: Yes
# Anticipated Findings: mothers speak more female-biased nouns in CDS to female infants than to male infants
# I may add another layer of point chart on the plot, showing data of each child

```
# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
