---
title             : "My Notebook"
shorttitle        : "from D2M course"

author: 
  - name          : "Katia Yang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "kaiweny@uchicago.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : html_document
---

```{r source-script}
source("My_Script.R")
```

<!-- Assignment 5 -->

```{r call-function}
# Call the hello_world function
result1 <- hello_world("Dr.Dowling")
result2 <- hello_world("Voldemort")
result3 <- hello_world("Wubalubadubdub")

# Print the results
print(result1)
print(result2)
print(result3)
```

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```


# dataset

```
6 Corpuses from the **CHILDES** 
URL:[<https://childes.talkbank.org/>]

## Material

## Participants

Participants including *6 children*:   
1. Alex  
   a. Alex's mother
2. Violet  
   a. Violet's father
3. Naima  
4. Lily  
5. William  
6. Ethan  

<!-- I don't know what to write --> 
And these characters: 

* Adventure Time
  - Finn
  - Jack
  - BMO
  - Princess Bubblegum
  - Ice King
* Rick and Morty
  - Rick
  - Morty
    + Morty 233
    + Morty 167
  - Summer

## Procedure

# Data analysis
## Assignment (10) & (12)
## 10.1 & 12.2
```{r Male-Biased Nouns plots}
# Data analysis
## Assignment (10) & (12)
## 10.1 & 12.2
library(ggplot2)
install.packages("reshape2")
library(reshape2)

m.data <- read.csv("//Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/Proportion data/noun_proportion_data.csv")

ggplot(m.data, aes(x = target_child_sex, y = mnoun_proportion, fill = target_child_sex)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.5, aes(colour = target_child_sex)) +
  scale_fill_manual(values = c("female" = "lightpink", "male" = "lightblue")) +
  labs(x = "Gender", y = "Proportion", title = "Male-Biased Noun Proportion") +
  theme_minimal()

### X-axis: The gloss variable, representing different words (like "dress", "doll", "necklace", etc.).
### Y-axis: The count or frequency of each word, indicating how often each word appears in the dataset.
### Type of Plot: Bar Chart. 
### Comparison Across Groups?: Yes
### Anticipated Findings: mothers speak more female-biased nouns to female infants than to male infants
```
###10.2
```{r mock up Female-biased Nouns Plot}

f.data <- read.csv("//Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/Proportion data/noun_proportion_data.csv")

plot_f.data <- ggplot(f.data, aes(x = target_child_sex, y = fnoun_proportion, fill = target_child_sex)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.5, aes(colour = target_child_sex)) +
  scale_fill_manual(values = c("female" = "lightpink", "male" = "lightblue")) +
  labs(x = "Gender", y = "Proportion", title = "Female-Biased Noun Proportion") +
  theme_minimal()
print(plot_f.data)

### X-axis: female/male infants
### Y-axis: counts of frequency of female-biased nouns
### Type of Plot: box plot
### Comparison Across Groups?: Yes
### Anticipated Findings: mothers speak more female-biased nouns in CDS to female infants than to male infants

```

```{r combined plot}
## Assignment (13). Prettified Plot
combined.data <- read.csv("//Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/Proportion data/noun_proportion_data.csv")

long_data <- combined.data %>%
  pivot_longer(cols = c(mnoun_proportion, fnoun_proportion),
               names_to = "type",
               values_to = "proportion")
labels_gender = c('fnoun_proportion' = "Female-Biased", 'mnoun_proportion' = "Male-Biased")

ggplot(long_data, aes(x = target_child_sex, y = proportion, fill = target_child_sex)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.5, aes(colour = target_child_sex)) +
  scale_fill_manual(values = c("female" = "lightpink", "male" = "lightblue")) +
  labs(x = "Gender", y = "Proportion") +
  facet_wrap(~type, scales = "fixed", labeller = as_labeller(labels_gender)) +
  labs(title = "Proportion of Gender-Biased Nouns")+
  theme(
  title = element_text(family = "Comic Sans MS"),
  axis.title = element_text(family = "Courier"),
  panel.grid = element_line(colour = "white", linetype = 3, size = .7),
  legend.title = element_text(family = "Courier", size = 10),
  strip.background = element_rect(fill = "gray60"),
  strip.text = element_text(colour = "white", family = "Courier", hjust = 0),
  legend.position = "bottom"
)
```

# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
