---
title             : "My Notebook"
shorttitle        : "from D2M course"

author: 
  - name          : "Katia Yang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "kaiweny@uchicago.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : html_document
---

```{r source-script}
source("My_Script.R")
```

<!-- Assignment 5 -->

```{r call-function}
# Call the hello_world function
result1 <- hello_world("Dr.Dowling")
result2 <- hello_world("Voldemort")
result3 <- hello_world("Wubalubadubdub")

# Print the results
print(result1)
print(result2)
print(result3)
```

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods

### dataset

PROVIDENCE CORPUS from the **CHILDES** URL:[<https://phon.talkbank.org/access/Eng-NA/Providence.html>]

## Material

## Participants

Participants including *6 children*:   

1. Alex  
   a. Alex's mother
2. Violet  
   a. Violet's father
3. Naima  
4. Lily  
5. William  
6. Ethan  

<!-- I don't know what to write --> 
And these characters: 

* Adventure Time
  - Finn
  - Jack
  - BMO
  - Princess Bubblegum
  - Ice King
* Rick and Morty
  - Rick
  - Morty
    + Morty 233
    + Morty 167
  - Summer

## Procedure

## Data analysis

We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
