---
title             : "My Notebook"
shorttitle        : "from D2M course"

author: 
  - name          : "Katia Yang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "kaiweny@uchicago.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : html_document
---

```{r source-script}
source("My_Script.R")
```

<!-- Assignment 5 -->

```{r call-function}
# Call the hello_world function
result1 <- hello_world("Dr.Dowling")
result2 <- hello_world("Voldemort")
result3 <- hello_world("Wubalubadubdub")

# Print the results
print(result1)
print(result2)
print(result3)
```

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```


# Methods

### dataset

```
PROVIDENCE CORPUS from the **CHILDES** URL:[<https://phon.talkbank.org/access/Eng-NA/Providence.html>]

## Material

## Participants

Participants including *6 children*:   

1. Alex  
   a. Alex's mother
2. Violet  
   a. Violet's father
3. Naima  
4. Lily  
5. William  
6. Ethan  

<!-- I don't know what to write --> 
And these characters: 

* Adventure Time
  - Finn
  - Jack
  - BMO
  - Princess Bubblegum
  - Ice King
* Rick and Morty
  - Rick
  - Morty
    + Morty 233
    + Morty 167
  - Summer

## Procedure

## Data analysis
### Assignment (10)
### 10.1
```{r mock up female biased nouns plots}
library(ggplot2)
install.packages("reshape2")
library(reshape2)

data <- read.csv("/Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/tidy data/counts_fnouns.csv")

long_data <- melt(data, id.vars = "gloss")

ggplot(long_data, aes(x = gloss, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_minimal() +
  labs(x = "Word", y = "Count", fill = "Gender",
       title = "Frequency of Female Gender-biased Nouns",
       subtitle = "Comparing the frequency of gender-biased maternal CDS between female and male infants") +
  scale_fill_manual(values = c("female" = "pink", "male" = "lightblue"))

# X-axis: The gloss variable, representing different words (like "dress", "doll", "necklace", etc.).
# Y-axis: The count or frequency of each word, indicating how often each word appears in the dataset.
# Type of Plot: Bar Chart. 
# Comparison Across Groups?: Yes
# Anticipated Findings: mothers speak more female-biased nouns to female infants than to male infants
```
###10.2
```{r mock up appearance-related adj.s}
app.data <- read.csv("/Users/katia/Desktop/D2M/CHILDES_utterance/Childes dataset/tidy data/final_app_adj.csv")

ggplot(data, aes(x = female, y = male, label = gloss)) +
  geom_point() +  
  geom_text(vjust = -1) +  
  theme_minimal() + 
  labs(x = "Female", y = "Male",
  title = "Frequency of Appearance-related Adj.",
  subtitle = "Comparing the frequency of gender-biased maternal CDS between female and male infants")

# X-axis: counts of frequency of appearance-related adj. spoken to female infants
# Y-axis: counts of frequency of appearance-related adj. spoken to male infants
# Type of Plot: Scatter Chart. (*I think Bar Chart suits better*)
# Comparison Across Groups?: Yes
# Anticipated Findings: mothers speak more appearance-related adj. to female infants than to male infants

```
# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
